---
title: "Logistic regression with mixed effects"
subtitle: "Ie AMP data where each multiple participants emit multiple dichotomous responses"
author: "Ian Hussey"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      cache.lazy=FALSE)
```

```{r}

# dependencies
library(tidyverse)
library(psych)
library(weights)  # for rd(), a round() alternative
library(plotrix)  # for std.error
library(lme4)
library(effects)
library(knitr)
library(kableExtra)
library(sjPlot)
library(apa)

# rounds all numerics in a df
round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))
  df[,nums] <- round(df[,nums], digits = digits)
  (df)
}

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999) 

```

# Hypothesis test 1: Differences in AMP effects between IAT contrast pair conditions

ie IAT_condition is a between subjects condition here

```{r}

AMP_data <- 
  read.csv("data/processed_data_mixed_effects.csv") %>%
  dplyr::filter(exclude == FALSE,
                IAT_exclude_based_on_fast_trials == FALSE) %>%
  dplyr::mutate(participant = as.factor(participant),
                rating_factor = as.factor(ifelse(accuracy == 0, "negative", 
                                                 ifelse(accuracy == 1, "positive", NA))),
                IAT_condition = as.factor(IAT_condition)) %>%
  dplyr::rename(prime_type = item,
                rating = accuracy)

# Check that variables that should be factors are indeed factors
sapply(AMP_data, class)

```

### Plot distribution

Distribution of AMP ratings.

```{r fig.height=3, fig.width=5}

AMP_participant_summary_data <-
  AMP_data %>%
  group_by(participant) %>%
  dplyr::summarize(perc_rating = round(mean(rating), 2))

ggplot(AMP_participant_summary_data, 
       aes(perc_rating)) + 
  geom_density(alpha=0.50) +
  theme_classic()

```

## Generalised linear mixed model

### Model

```{r}

# convergence issues with model apparently due to scale of continuous variable, so standardize and center it.
# https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html

model_1 <- glmer(rating ~ prime_type * IAT_condition + (1 | participant), 
                 family = "binomial",
                 contrasts = list(prime_type = "contr.sum", 
                                  IAT_condition = "contr.sum"),
                 data = AMP_data)

```

### Summary

```{r message=FALSE, warning=FALSE}

sjt.glmer(model_1, 
          emph.p = FALSE,
          digits.p = 7)

```

### Bootstrap ORs

For key parameters of interest

```{r}

# apply fixef() to the output of each boot to get fixed effects, save only this to the data frame
model_1_boot <- bootMer(model_1, 
                        FUN = fixef,  
                        nsim = 1000,
                        parallel = "multicore")

model_1_boot %>%
  as.data.frame() %>%
  # exponentiate to convert log odds to odds ratios
  dplyr::summarize(interaction_OR_mean   = mean(exp(prime_type1:IAT_condition1), na.rm = TRUE),  
                   interaction_OR_median = quantile(exp(prime_type1:IAT_condition1), 0.500, na.rm = TRUE),  
                   interaction_OR_lwr    = quantile(exp(prime_type1:IAT_condition1), 0.025, na.rm = TRUE),
                   interaction_OR_upr    = quantile(exp(prime_type1:IAT_condition1), 0.975, na.rm = TRUE)) %>%
  round_df(10) %>%
  gather()

# write to disk given long runtime
save(model_1_boot, file = "data/models/model_1_boot.RData")
load("data/models/model_1_boot.RData")

```

### Model performance

```{r}

# model performance
# add model predictions back to the original data frame
AMP_data$predicted_probability <- predict(model_1, type = "response")

# model performance: AUC
## custom function to do this via exact test. PIM etc would estimate this far more quickly, but somewhat black boxes some assumptions.
ruscios_A <- function(variable, group, data, value1 = 1, value2 = 0) {
  # Ensure data is a data frame (e.g., not a tbl_data)
  data <- as.data.frame(data)
  # Select the observations for group 1
  x <- data[data[[group]] == value1, variable]
  # Select the observations for group 2
  y <- data[data[[group]] == value2, variable]
  # Matrix with difference between XY for all pairs (Guillaume Rousselet's suggestion)
  m <- outer(x, y, FUN = "-")
  # Convert to booleans; count ties as half true.
  m <- ifelse(m == 0, 0.5, m > 0)
  # Return proportion of TRUEs
  ruscios_A <- round(mean(m), 3)
  return(as.numeric(ruscios_A))
}

# ruscios_A_boot <- function(data, variable, group, value1 = 1, value2 = 0, B = 1000) {
#   require(tidyverse)
#   require(broom)
#   ruscios_A_results <- data %>%
#     ruscios_A(variable = variable,
#               group = group,
#               value1 = value1,
#               value2 = value2,
#               data = .)
#   
#   ruscios_A_boot_results <- data %>%
#     broom::bootstrap(B) %>%
#     do(broom::tidy(ruscios_A(variable = variable,
#                              group = group,
#                              value1 = value1,
#                              value2 = value2,
#                              data = .))) %>%
#     ungroup() %>%
#     dplyr::summarize(AUC_ci_lwr = round(quantile(x, 0.025, na.rm = TRUE), 3),
#                      AUC_ci_upr = round(quantile(x, 0.975, na.rm = TRUE), 3)) %>%
#     mutate(AUC_estimate = ruscios_A_results)
#   
#   return(ruscios_A_boot_results)
# }

AUC_with_CIs <- ruscios_A(data = AMP_data, 
                          variable = "predicted_probability", 
                          group = "rating")

# - bootstrapping of CIs possible using above function, but runtime is extremely long (hours)

```

Model AUC `r AUC_with_CIs`.

### Plot effects

```{r fig.height=3, fig.width=5}

sjp.glmer(model_1, 
          type = "fe")

```

### Table predictions

Probabilities (of positive rating of prime) for each condition. NB probability = Odds Ratio / (1 + Odds Ratio). 

```{r fig.height=3, fig.width=5}

model_1_predicted_effects <- 
  as.data.frame(effect("prime_type:IAT_condition", model_1)) %>%
  dplyr::rename(`IAT condition` = IAT_condition,
                `AMP prime type` = prime_type)

model_1_predicted_effects %>% 
  round_df(2) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```
  
### Plot predictions

```{r fig.height=5, fig.width=8}

ggplot(data = model_1_predicted_effects,
       aes(x = `AMP prime type`, y = fit, colour = `IAT condition`)) +
  geom_pointrange(aes(ymax = upper,
                      ymin = lower),
                  position = position_dodge(width = .1)) +
  geom_line(aes(group = `IAT condition`),
            position = position_dodge(width = .1)) +
  ylab("Probability of rating prime positively") +
  xlab("Prime type") +
  scale_colour_grey() +
  theme_classic()

```

NB Ideally I'd add some AUC calculations for the model as a whole, as well as logistic regression plots for the fixed effects, as in the fixed effects analysis.  


